A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-03-10 paper/draft.tex
ad who benefits

The \emph{RAIS} data is structured as follows. Each row corresponds to a job associated to a worker, which may or may not appear more than once in the dataset -- since workers can hold multiple jobs at the same time. Each worker is tagged by a unique national id, the \emph{CPF}, which allows for following workers across sectors and over time. Additionally, the identified \emph{RAIS} contains the names and dates of birth of workers.\footnote{Access to the identified \emph{RAIS} was generously provided by the Department of Economics at Princeton University, hosted at the Industrial Relations office.} These are the unique primary keys that make possible join this dataset to other sources of data. Other studies have leveraged similar join approaches to infer employment benefits of campaign contributors \citep{colonnelli2018patronage}, as well as whether party members receive public sector employment if they belong to the same party as the winning mayor \citep{brollo2017victor}.

@@

>>>>

The \emph{RAIS} data is structured as follows. Each row corresponds to a job associated to a worker, which may or may not appear more than once in the dataset -- since workers can hold multiple jobs at the same time. Each worker is tagged by a unique national id, the \emph{CPF}, which allows for following workers across sectors and over time. Additionally, the identified \emph{RAIS} contains the names and dates of birth of workers.\footnote{Access to the identified \emph{RAIS} was generously provided by the Department of Economics at Princeton University, hosted at the Industrial Relations Office.} These are the unique primary keys that make possible join this dataset to other sources of data. Other studies have leveraged similar join approaches to infer employment benefits of campaign contributors \citep{colonnelli2018patronage}, as well as whether party members receive public sector employment if they belong to the same party as the winning mayor \citep{brollo2017victor}.

@@

\subsection{Who benefits from patronage?}

Who should politicians buy off: rich or poor voters? There are competing views on who benefits from patronage. On the one hand, from a politician's perspective it would be cheaper to buy voters who are poor, insofar as the return on investment would be greater for poorer voters, who need and value more monetary incentives \citet{stokes2013brokers}. Other scholars argue that in order to maximize electoral returns, politicians target swing voters, those who are indifferent to either party and therefore, again, require the least resources to buy off \citet{dixit1996determinants}.

On the other, there are good reasons to expect politicians to target rich voters as well. There is a well-established literature on money and politics,
